\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{fontawesome5}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{makecell}


\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage[margin=1.4cm]{geometry}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{12pt}


\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


\pdfgentounicode=1


\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{0pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \parbox[t]{0.8\textwidth}{\small #1} & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{0pt}}

\begin{document}

\begin{center}
    {\Large \scshape Dr. Tarit Bhattacharya} \\[2mm]
    \faGraduationCap\ Doctor of Philosophy - Physical Education \\[2mm]
    \faPhone\ +91 9433083645 ~ 
    \faEnvelope\ \href{mailto:taritbhatt2007@gmail.com}{taritbhatt2007@gmail.com} \\
    \faMapMarker\ 77 Dharampur, Nonapukur, Chinsurah, Hooghly 
    \vspace{-8pt}
\end{center}

\section{Summary}
  \resumeSubHeadingListStart
    \resumeItem{Dr. Tarit Bhattacharya is a highly experienced professional in physical education, holding a doctorate degree, with about 28 years of teaching experience. He has served as an assistant teacher and lecturer at various esteemed institutions including Birla High School, Jadavpur University, and Rajhat High School. He also possesses significant volunteering experience in similar capacities.}
  \resumeSubHeadingListEnd

\section{Education \& Qualifications}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Kalyani}{2010}
      {Ph.D. in Physical Education}{}
    \resumeSubheading
      {Annamalai University}{2007}
      {Master of Philosophy (M.Phil) in Physical Education, 1st Class}{Tamil Nadu}
    \resumeSubheading
      {Kalyani University}{1997}
      {Master of Physical Education (M.P.Ed), 1st Class}{}
    \resumeSubheading
      {Kalyani University}{1995}
      {Bachelor of Physical Education (B.P.Ed), 1st Class}{}
    \resumeSubheading
      {UGC NET Examination}{1999}
      {UGC NET Qualified in Physical Education}{}
  \resumeSubHeadingListEnd

\section{Experience (Teaching \& Research)}
  \resumeSubHeadingListStart
    \resumeSubheading{Rajhat High School}{25+ Years}
      {Assistant Teacher in Physical Education}{Kolkata}
    \resumeSubheading{Jadavpur University}{2 Years}
      {Assistant Lecturer in Physical Education}{Kolkata}
    \resumeSubheading{Birla High School}{2 Years}
      {Assistant Teacher in Physical Education}{Kolkata}
    \resumeSubheading{University of Kalyani}{2010}
      {Student \& Research Scholar}{Kalyani, West Bengal}
    \resumeSubheading{Annamalai University}{2007}
      {Master of Philosophy}{Tamil Nadu}
    \resumeSubheading{University of Burdwan}{1988}
      {Championship in Football (Winner, State \& University Level)}{West Bengal}
    \resumeSubheading{National Conference on Trends and Practices in Physical Education}{2010}
      {Paper Publication}{Visva Bharati}
  \resumeSubHeadingListEnd

\section{Career Highlights}
  \resumeSubHeadingListStart
    \resumeItem{Served as assistant teacher and lecturer at Birla High School, Jadavpur University, and Rajhat High School. He was appointed to the post of district organizer of physical education, Jalpaiguri in April 2000, but did not join due to personal reasons. Similarly, he was offered the position of university research scholar (JRF full-time), faculty of education, Kalyani University in December 1997, but did not accept the position due to personal reasons.}
    \resumeItem{He has experience to officiate different athlete meet as a member of the Sports Officials' Association Hooghly, and gave a radio talk show on sports and games from Paschimbanga Rajya Sishu Shiksha Mission. He participated in university level football championship and gained the winner position for the University of Burdwan in 1988.}
  \resumeSubHeadingListEnd

\section{Skills}
  \begin{multicols}{2}
  \begin{itemize}[leftmargin=0.2in, label={$\bullet$}]
    \small{\item{Public Speaking}}
    \small{\item{Fitness Coaching (Professional level)}}
    \small{\item{Wellness (Professional level)}}
    \small{\item{Certified Yoga Guide (Legitimate)}}
    \small{\item{Former District level Football Player (Legitimate)}}
    \small{\item{Former University level Football Player (Legitimate)}}
    \small{\item{Lifestyle \& Wellness Management (Professional)}}
  \end{itemize}
  \end{multicols}
  \vspace{10pt}

\section{Interests}
  \begin{multicols}{2}
  \begin{itemize}[leftmargin=0.2in, label={$\bullet$}]
    \small{\item{Football}}
    \small{\item{Yoga}}
    \small{\item{Physical Fitness}}
    \small{\item{Lifestyle \& Wellness Management}}
    \small{\item{Diet \& Food Management}}
    \small{\item{Teaching \& Mentoring}}
  \end{itemize}
  \end{multicols}
  \vspace{10pt}

\section{Publications}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Psychophysical Reactivity Among Indian Female Traditional and Creative Dancers}}
      {2010}
    \resumeItemListStart
      \resumeItem{Submitted to Kalyani University.}
    \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Performance Evaluation Of 3 Groups of Indian Female Dancers}}
      {2007}
    \resumeItemListStart
      \resumeItem{Published at Annamalai University.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Certifications \& Awards}
  \resumeSubHeadingListStart
    \resumeItem{Junior Inter District Football Tournament, Hooghly District Sports Association (December 1983).}
    \resumeItem{Inter College Football Championship, University of Burdwan (October 1988).}
    \resumeItem{Football Championship Winner, University of Burdwan (1988).}
    \resumeItem{2nd Runners up in YMCA, Calcutta YMCA (February 1988).}
    \resumeItem{Young Men's Christian Association, Calcutta YMCA (February 1998).}
    \resumeItem{UGC NET Qualified, UGC NET (1999).}
    \resumeItem{Residential Central Refresher Course, West Bengal School Sports Association (June 2001).}
    \resumeItem{National Seminar on Molecular Physiology, University of Kalyani (February 2002).}
    \resumeItem{Presented Research Paper in Molecular Physiology, University of Kalyani (February 2002).}
    \resumeItem{Physiotherapy Certificate Course, Institution of Public Health Engineers' (2002).}
    \resumeItem{Passed the Final Examination of Physiotherapy Course, Institution of Public Health Engineers' India (February 2003).}
    \resumeItem{National Seminar on Physical Education, Kalyani University (November 2005).}
    \resumeItem{Presented a Paper in National Seminar on HR Development in 21st Century, University of Kalyani (November 2005).}
    \resumeItem{Master of Philosophy in Physical Education, Annamalai University (September 2007).}
    \resumeItem{State Level Seminar, Women's College (January 2008).}
    \resumeItem{Role of Sports Medicine, Sports Medcon 2008 (January 2008).}
    \resumeItem{Attended Role of Sports Medicine, Sports Medcon 2008 (January 2008).}
    \resumeItem{National Conference on Trends and Practices in Physical Education, Visva Bharati University (January 2010).}
    \resumeItem{Ph.D. in Physical Education, University of Kalyani (February 2010).}
  \resumeSubHeadingListEnd

\section{Languages}
 \begin{itemize}[label={}]
    \small{\item{
     \textbf{Bengali}{: Vernacular} \\[1mm]
     \textbf{English}{: Professional} \\[1mm]
     \textbf{Hindi}{: Intermediate}
    }}
 \end{itemize}

\section{Volunteering}
  \resumeSubHeadingListStart
    \resumeSubheading{Rajhat High School}{25+ Years}
      {Senior Faculty}{West Bengal}
    \resumeSubheading{Jadavpur University}{2+ Years}
      {Assistant Lecturer}{Kolkata}
    \resumeSubheading{Birla High School}{2 Years}
      {Assistant Faculty Physical Education}{Kolkata}
  \resumeSubHeadingListEnd

\end{document}